---
title: 'STAT 5730: Exam'
author: Jin Gyu Kim
output: prettydoc::html_pretty
---

```{r setup, include=FALSE}
# Keep this chunk at the top of the exam. 
# DO NOT MODIFY

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(nycflights13)

# This code seeds the randomization for your personalized exam using your 
# OSU `name.n`. Replace `vu.104` below with your OSU `name.n`. Do not modify 
# anything else.

my_name_dot_n <- "kim.6182" # REPLACE WITH YOUR NAME.N

set.seed(prod(strtoi(charToRaw(my_name_dot_n), 16L)) %% 2e9)
datasets <- c("airlines", "airports", "flights", "planes", "weather")
flights <- flights[, sample(ncol(flights))]
destination <- flights %>% 
  group_by(dest) %>%
  summarize(n_origin = n_distinct(origin)) %>%
  filter(n_origin == 2) %>% 
  left_join(airports, by = c("dest" = "faa")) %>%
  sample_n(size = 1)
```

-------------------------------------------------------------------------------

# Instructions

Read and follow these instructions __carefully__.  Points will be deducted 
if you do not follow the instructions. Submit (1) `exam.Rmd` file and (2) its 
knitted HTML output after reading and completing the following.

-   Enter your name in the `author:` field at the top of this file by replacing 
    `YOUR NAME HERE`.
-   This exam is __randomized__ and __personalized__. Make sure you follow 
    these steps exactly:
    1.  Enter your `name.n` above where it says `# REPLACE WITH YOUR NAME.N`. 
        I've included my `name.n` as an example.  
    2.  Knit the exam once to get your personalized exam HTML, make a copy of 
        that HTML and view it to get your personalized problems.
    3.  Enter your answers in this `.Rmd` file and submit (1) it and its (2) 
        knitted HTML output.
-   Do not modify any other headers or the section headers. Leave everything 
    alone, except where your answers go, e.g. __Replace__ `# YOUR CODE HERE` and
    `> YOUR EXPLANATION HERE`.
-   Complete the 20 problems in the "Problems" section below. 
    Some of these problems involve the 
    `nycflights13::flights` data.  The `nycflights13` and `tidyverse` packages 
    will be loaded for you at the top of the R Markdown file.
-   All plots must be made using `ggplot2` and displayed in your output HTML. 
    __Do not load any other libraries__.
-   For each problem you must provide __both__
    R code in the empty code chunk (if needed) __and__ 
    a human-readable explanation in complete English sentences immediately 
    below the code chunk. __Be sure to explain how you got your answer for 
    full credit.__
-   Formatting will be graded. __Be careful about keeping an empty line__ after 
    the R code chunk whenever you have a plot. Use back ticks to format 
    inline R code where appropriate.  Two examples are shown immediately below.

-------------------------------------------------------------------------------

## Example 1
How many rows does `flights` have?

```{r example1}
nrow(flights)
```

`flights` has `r nrow(flights)` rows.

## Example 2
Make a histogram of departure delays.  What do you notice about the plot?

```{r example2}
ggplot(data = flights, aes(x = dep_delay)) +
  geom_histogram()
```

The histogram has a long right tail, because there are some flights with 
extreme large departure delays.

-------------------------------------------------------------------------------

# Personalized exam for `r my_name_dot_n`

## Problem 1
How many rows and columns does __`r sample(datasets, size = 1)`__ have?

```{r problem1}
nrow(weather)
ncol(weather)
```

`Weather` has
rows = 26115
columns = 15

## Problem 2
What are the names of the columns of __`r sample(datasets, size = 1)`__? 
What are the types? How can you tell?

```{r problem2}
summary(weather)
typeof(weather)
```

Columns: `year`, `month`, `day`, `hour`, `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visib`, `time_hour`  
The data structure of `weather` is a list. List is a vector that allows its elements to have different types. it is indexed like vectors.

## Problem 3
How many flights __`r sample(c("arrived", "departed"), size = 1)`__ 
on-time or __`r sample(c("earlier", "later"), size = 1)`__?

```{r problem3}
not_canceled <- filter(flights, !is.na(dep_delay), !is.na(arr_delay))
summarize(not_canceled, n_really_delayed = sum(dep_delay >= 0))
```

There are 144211 of flights departed on time or later. 

## Problem 4
What is the RStudio keyboard shortcut for inserting the pipe operator `%>%`?
How did you find this out?

```{r problem4}
# NO CODE NECESSARY 
```

Shortcut for %>%: __For Mac__ - `control + shift + m`.
I found out from the lecture.

## Problem 5
Use `knitr::kable()` to print a table of the last __`r 2 + rpois(1, 10)`__ 
rows of `flights`.

```{r problem5}
library(knitr)
last_13_flights <- tail(flights, 13)
kable(last_13_flights)
```

I used tail to extract the last 13 flights, and use `kable` function to show my output of the last 13 data.

## Problem 6
Uncomment the following code and fix it so it works.

```{r problem6}
flights %>%
  select(year:day, ends_with("_delay"), dest) %>%
  filter(dest == "CMH")
```

I had to put `dest` variable in select to use the `filter` function. The `filter` function cannot be used when there is no data shown after select.

## Problem 7
What is the _type_ and _value_ of the expression 
__`r sample(c("x <- NA", "y <- TRUE", "x <- NA == 0"), size = 1)`__

```{r problem7}
typeof(x <- NA == 0)
x
```

The type of this expression is logical, and the value of the expression is NA since the missing value

## Problem 8
Fix the following plot so that (1) the smooth line is 
__`r sample(c("black", "purple", "green", "blue"), size = 1)`__ and (2) the 
confidence band (shaded ribbon) has a confidence level of 
__`r sample(seq(80,95, by = 5), size = 1)`%__.

```{r problem8}
 ggplot(data = mpg, aes(displ, hwy)) +
   geom_point() +
   geom_smooth(color = "green", level = 0.90)
```

I removed `aes()` from geom_smooth because it randomly assigns the color if we put `color = "green"` argument in the aes function. I put an argument `level = 0.90` to make a confidence band has a confidence level of 90% instead of default 95%. 

## Problem 9
What variables does 
__`r sample(c("stat_boxplot()", "stat_bin()", "stat_count()"), size = 1)`__ 
compute?

```{r problem9}
# NO CODE NECESSARY
```

`stat_boxplot()` has computed variables `width`, `ymin` or `xmin`, `lower` or `xlower`, `notchlower`, `middle` or `xmiddle`, `notchupper`, `upper` or `xupper`, `ymax` or `xmax`.  

## Problem 10
Why is it a bad idea to install R packages, e.g. with `install.packages()` 
in an R Markdown file?

```{r problem10}
# NO CODE NECESSARY
```

It is bad a bad idea to install R packages with `install.packages()` because it is not necessary to repeatedly install the package again when using rmd file. Once the installation of the package is done, it should be stayed in the library unless edited. Using install packages through a R markdown will probably compile several timesm, which is a bad idea.

## Problem 11
Uncomment the following code and explain all that is wrong, explain 
what needs to be done, and fix it. See also Problem 10.

```{r problem11}
ggplot(mpg, aes(displ, hwy)) +
  geom_quantile() +
  geom_point()
```

the `+` needs to be moved up, and the `geom_quantile()`, `geom_point()` should be inside of the ggplot function by using `tab`. 
For Problem 10, it should be altered to 'library()'.

## Problem 12
Make a sideways parallel box plot so that `manufacturer` is on the 
vertical axis and __`r sample(c("hwy", "cty"), size = 1)`__ is on the 
horizontal axis.

```{r problem12}
ggplot(mpg, aes(x = manufacturer, y = cty)) + 
  geom_boxplot() +
  coord_flip()
```

I used `coord_flip()` for switching x and y axes.

## Problem 13
Make a parallel box plot of __`r sample(c("departure", "arrival"), size = 1)`__
delay by hour based on flights 
that __`r sample(c("arrived", "departed"), size = 1)`__ late. 
The plot should use a log scale for departure/arrival delay and there should be one 
box for each value of `hour`.

```{r problem13}
late_flights <- filter(not_canceled, dep_delay > 0)
by_hour <- group_by(late_flights, hour) 
delayed_flights1 <- summarize(by_hour, arr_delay)

ggplot(delayed_flights1, aes(hour, arr_delay, group = hour)) +
  geom_boxplot() +
  scale_y_log10() +
  scale_x_continuous(breaks = 5:24)
```

I tried to filter flights that departed late than the scheduled departure time. Then I grouped the filtered flights with hour, summarizing arrival delays so I can have two variable. Then I made a ggplot x as a departure hour and y as a minutes of arrival dealy. 19 groups of hour was made and each hour had their own boxplot.

## Problem 14
Modify the following plot so that the facets are labeled with the 
corresponding variable names (`drv` and `cyl`).

```{r problem14}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(rows = vars(drv), cols = vars(cyl), labeller = label_both)
```

I added `labeller = label_both` to label the facet_grids at the end of the facet_grid function. 

## Problem 15
How many flights were scheduled to fly to 
__`r sample(unique(flights$dest), size = 1)`__ in 
__`r sample(month.name[1:6], size = 1)`--`r sample(month.name[7:12], size = 1)`__, 
2013? What proportion of these flights never 
__`r sample(c("arrived", "departed"), size = 1)`__?


```{r problem15}
to_ANC <- flights %>%
  filter(dest == "ANC") %>% 
  filter(month %in% c(4,5,6,7,8))

never_departed <- filter(to_ANC, is.na(air_time))

to_ANC

never_departed
```

I filtered out the destination to ANC, and months between 4,5,6,7, and 8 and showed 8 data all between July and August. I tried to filter never departed but there was no never departed flights from the filtered value. The proportion is 0 out of 8. -> 0%

## Problem 16
Which month had the highest __`r sample(c("proportion", "number"), size = 1)`__ 
of __`r sample(c("on-time", "late"), size = 1)`__ departures? Which month had 
the lowest?

```{r problem16}
on_time_departure <- not_canceled %>% 
  filter(dep_delay == 0) %>% 
  group_by(month) %>% 
  summarize(dep_delay = n()) %>% 
  arrange(desc(dep_delay))

on_time_departure
```

I defined the on time departure as zero hour departure delay by using filter function. Not early or later. I grouped by group and summarized the number of zero hour departure delay(on time). The most on time flight was on August(1537) and the least on time flight was Feburary(1164)

## Problem 17
What were the __`r 2 + rpois(1, 3)`__ 
__`r sample(c("most", "least"), size = 1)`__ frequently flown routes 
(`origin` and `dest` pairs)?

```{r problem17}
most_pairs <- flights %>% 
  group_by(origin, dest) %>% 
  summarize(n_most_pairs = n()) %>% 
  arrange(desc(n_most_pairs))

most_pairs
```

The 3 most frequent flown routes are:
JFK -> LAX 11262
LGA -> ATL 10263
LGA -> ORD 8857

## Problem 18
Make a bar chart showing the average departure delay (based on `not_cancelled` 
flights) by __`r sample(c("month", "hour"), size = 1)`__.

```{r problem18}
not_cancelled <- filter(flights, !is.na(dep_delay))

monthly_delay <- group_by(not_cancelled, month) %>% 
  summarize(avg_dep_delay = mean(dep_delay)) 

ggplot(monthly_delay) +
  geom_bar(aes(month, avg_dep_delay), stat='identity') +
  scale_x_continuous(breaks = 1:12)
```

I grouped month from `not_cancelled` and summarized the `dep_delay` as the average. Then created a geom_bar to show the average departure delay by month

## Problem 19
The New York City area has two airports that operate flights to 
__`r destination$dest` (`r destination$name`)__. 
Make a plot comparing the distributions of travel times (define this) to 
`r destination$dest`. The plot should show histograms (with appropriate choice of 
binwidth) and display summaries such as the median or mean as additional 
layers on the plot.  The rest of the design of the plot is up to you, but 
you should make reasonable choices and provide a justification for your 
choices.

```{r problem19}
dsm_flights <- filter(not_canceled, dest == 'DSM') %>% 
  group_by(origin, air_time) %>% 
  summarize(n_flights = n())

mean_flights <- filter(not_canceled, dest == 'DSM') %>% 
  group_by(origin) %>%
  summarize(mean_value = mean(air_time))

mean_flights

ggplot(dsm_flights, aes(air_time, n_flights, fill = origin)) +
  geom_histogram(color = 'black', binwidth = 10, position = 'stack', stat = 'identity') +
  geom_vline(data = mean_flights, aes(xintercept = mean_value, color = origin), linetype = 5)
```

I made a histogram counting number of flights distributed of `air_time` with a bandwidth of 10 displaying the mean of `air_time` origin of EWR, and LGA. The average flight time for EWR is 149.5410, and LGA 146.1504, which concludes a trip from LGA can same 3 minutes in average. However, the number of samples from LGA is much less than EWR.

## Problem 20
How does the number of cancelled flights vary by origin and month? Are there 
more cancelled flights during certain months than others? Does that vary 
across origins? Does it matter if you look at the proportion (number cancelled 
divided by total number of flights for that origin) instead of number? Make a 
plot (or two if you wish) to answer these questions, and comment on how your 
plot answers these questions.

```{r problem20}
# By total stack
by_month <- filter(flights, is.na(air_time)) %>% 
  group_by(month, origin) %>% 
  summarize(n_no_flights = n()) 

ggplot(by_month, aes(month, n_no_flights, fill = origin)) +
  geom_bar(position = 'dodge', stat = 'identity') +
  scale_x_continuous(breaks = 1:12)

# By fill
ggplot(by_month, aes(x = month, y = n_no_flights, fill = origin)) +
  geom_bar(position = "fill", stat = 'identity') +
  scale_x_continuous(breaks = 1:12)
```

EWR had more cancelled flights significantly during winter(Dec, Jan, Feb). LGA had more cancelled flights significantly during autumn(July, Aug, Sept). It matters if I look at the proportion instaed of number because it is easy to find how much the origin takes place in one month. 
