---
title: "homework-03"
author: "Jin Gyu Kim"
date: "2/4/2022"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#HoPR Exercises

## HoPR 5.1 
```{r}
character <- c("1", "one")
typeof(character)

number <- c(1)
typeof(number)
```

# HoPR 5.2
```{r}
hand <- c("ace", "king", "queen", "jack", "ten")

typeof(hand)

names(hand) <- c("spade", "spade", "spade",
"spade", "spade")

hand
```

# HoPR 5.3
```{r}
royal_flush <- c("ace", "king", "queen", "jack", "ten", "spades", "spades", "spades", "spades", "spades")
r <- matrix(royal_flush, nrow = 5)
r
```

# HoPR 5.4
The vector results of assigning everything as a character. Since atomic vector can only save as one type of data
```{r}
card <- c("ace", "hearts", 1)
card

typeof(card)
```

# HoPR 5.5
```{r}
card1 <- list("king", "clover", 10)
card1
typeof(card1)
```

# Additional exercises

## Exercise 1
```{r}
TRUE == T
T <- 55
TRUE == T
```

The first line is set as Boolean value so it comes out as true, but the second line sets "T" as a double. So the third line comes out as FALSE. To avoid problems, do not set confusing words as variables. Use "card" as a variable instead of "TRUE"

## Exercise 2
```{r}
library(ggplot2)
p <- ggplot(data = mpg) + 
    geom_point(mapping = aes(x = displ, y = hwy))
typeof(p)
length(p)
names(p)
attributes(p)
```
1. p is a list. The length is 9
2. "data", "layers", "scales", "mapping", "theme", "coordinates", "facet", "plot_env", "labels" 
3. $names "data", "layers", "scales", "mapping", "theme", "coordinates", "facet", "plot_env", "labels" 
$class "gg", "ggplot"

## Exercise 3
log(x = 10) and log(x <- 10) both are assigning an object and both values comes out the same. But = is only allowed to assign arguments but not functions
```{r}
value <- (x <- 10)
value
typeof(value[1])
log(x = 10)
log(x <- 10)
```

## Exercise 4 
the function ls() returns the list the names of all the objects that are present in the working directory. rm() function removes from the list of the global environment
```{r}
height <- 66
feet <- height %% 12 #integer division 
ls()

rm(height)
```

## Exercise 5
Doubles are subject to rounding error. The computer does not interpret value left and right the same.
```{r}
(0.18 - 0.08) == 0.1

all.equal(0.18 - 0.08, 0.1) 
```

## Exercise 6
```{r}
my_list <-list(mean = 0, sd = 1, distribution = 'normal')
my_list$sample <- rnorm(10)
# my_list[['sample']] <- rnorm(10)
sample(my_list)
```

## Exercise 7
carat = 2.29, price = 18823
```{r}
library(ggplot2)

max.id <- diamonds$price == max(diamonds$price)

max(diamonds$price)

diamonds$carat[max.id]
```

## Exercise 8
5222 of diamonds has greater price than 10000
```{r}
sum_diamond <- diamonds$price > 10000
sum(sum_diamond)
```

## Exercise 9
If pasting a character and numeric vector together, the computer will automatically assign all the elements as characters. 
```{r}
exercise9 <- c(1, "one")
typeof(exercise9)
```

## Exercise 10
1.
```{r}
caratz <- ((diamonds$carat - mean(diamonds$carat)))/sd(diamonds$carat)

scale(diamonds$carat)

ggplot(data = diamonds, mapping = aes(x = scale(diamonds$carat), y = caratz)) +
  geom_point()
```
2. arguments of scale():
x - a numeric matrix
center - either a logical value or numeric-alike vector of length equal to the number of columns of x
scale - either a logical value or a numeric-alike vector of length equal to the number of columns of x.

```{r}
#center a vector by subtracting its mean only
scale(diamonds$carat, scale = FALSE)
  
#center a vector by subtracting its mean only
scale(diamonds$carat, center = FALSE)
```

## Exercise 11
```{r}
# Use indexing by a character to extract the columns of mpg named hwy and cty. 
mpg[, c('cty', 'hwy')]
class(mpg[, c('cty', 'hwy')])
```

## Exercise 12
```{r}
# Copy mpg to another variable named mpg_copy
mpg_copy <- mpg

# Use names() to rename the columns cty and hwy of mpg_copy to city and highway, respectively.
names(mpg_copy)[names(mpg_copy) == 'cty'] <- 'city'
names(mpg_copy)[names(mpg_copy) == 'hwy'] <- 'highway'

mpg_copy[, c('city', 'highway')]
```

## Exercise 13
x is a matrix which means the elements are arranged in a two-dimensional rectangular layout. They contain elements of the same atomic types. x[,1] is not a matrix because it is not a two-dimensional rectangular layout, but only giving numeric values.
```{r}
# What is the following object?
x <- matrix(rnorm(200), nrow = 20, ncol = 10)
class(x)

# Verify that the following object is not a matrix.
x[,1]
class(x[,1])
```

## Exercise 14
2. The previous plot is incorrect because the rain amount shows in negative value
4. The pattern shows sudden increase after 2000 days, and gradual decrease after then
```{r}
# Make a scatterplot of rain against day.
library(ggplot2)
require(readr)
rainfall <- read_csv(file = "http://www.stat.osu.edu/~vqv/4194/data/rainfall.csv")

ggplot(data = rainfall, mapping = aes(x = day, y = rain)) +
  geom_point()

# Fix the data with NA and create a new plot of rain against day.
rainfall$rain[rainfall$rain < 0] <- NA

ggplot(data = rainfall, mapping = aes(x = day, y = rain)) +
  geom_point()

#Make a plot showing days for where the rain measurement is missing. Does there appear to be a pattern to the missingness? Explain using your plot.
ggplot(data = rainfall[is.na(rainfall$rain), ], mapping = aes(x = day, y = is.na(rain))) +
  geom_point() +
  geom_violin()

```

