---
title: "homework-04"
author: "Jin Gyu Kim"
date: "2/10/2022"
output: html_document
---

#R4DS Exercises

```{r}
library(nycflights13)
library(tidyverse)
```

## R4DS 5.2.4

### Exercise 1
Find all flights that 

Had an arrival delay of two or more hours

```r
filter(flights, arr_delay >= 2 * 60)
```

Flew to Houston (IAH or HOU)

```r
filter(flights, dest == "IAH" | dest == "HOU")
```

Were operated by United, American, or Delta

```r
filter(flights, carrier %in% c("UA", "AA", "DL"))
```

Departed in summer (July, August, and September)

```r
filter(flights, month %in% c(7, 8, 9))
```

Arrived more than two hours late, but didn’t leave late

```r
filter(flights, dep_delay < 1 & arr_delay > 120)
```

Were delayed by at least an hour, but made up over 30 minutes in flight

```r
filter(flights, dep_delay > 60 & dep_delay - arr_delay > 30)
```

Departed between midnight and 6am (inclusive)

```r
filter(flights, dep_time %in% c(0:600))
```

### Exercise 2

```{r}
# Departed in summer (July, August, and September)
filter(flights, between(month, 7, 9))

#Departed between midnight and 6am (inclusive)
filter(flights, between(dep_time, 0, 600))
```

### Exercise 3

```{r}
filter(flights, is.na(dep_time))
```
There are 8,225 flights have a missing dep_time. dep_delay, arr_time, arr_delay, air_time is also missing in the observations. These rows representing whether the flight has actually fled. Missing data shows that 8,225 flights has been cancelled.

### Exercise 4

```{r}
# NA ^ 0 is not missing because even if we don't know the value, power of 0 always represents 1
NA ^ 0

# This statement is saying 'NA or True'. Even NA doesn't have a value the statement 'OR' made the return as TRUE 
NA | TRUE

# Anything and FALSE returns as FALSE. 
FALSE & NA
```


## R4DS 5.3.1

### Exercise 1

```{r}
arrange(flights, desc(is.na(dep_time), is.na(dep_delay), is.na(arr_time), is.na(arr_delay), is.na(air_time)))
```

### Exercise 2

```{r}
# most delayed flight
arrange(flights, desc(dep_delay))

# most earliest flight
arrange(flights, dep_delay)
```

### Exercise 3

```{r}
flight_time <- mutate(flights, speed = distance/ air_time * 60)

arrange(flight_time, desc(speed))
```

### Exercise 4

```{r}
# Flights traveled farthest
arrange(flights, desc(distance))

# Flights traveled shortest
arrange(flights, distance)

```

## R4DS 5.4.1

### Exercise 1

```{r}
#1st way
select(flights, starts_with("arr") | starts_with("dep"))

#2nd way
select(flights, dep_time, arr_time | ends_with("delay"))

#3rd way
select(flights, dep_time, dep_delay, arr_time, arr_delay)
```

### Exercise 2

```{r}
select(flights, dep_time, dep_time, dep_time)
```
It doesn't repeat the variable even if you put a variable multiple times. It only shows once.

### Exercise 3

```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, any_of(vars))
```
### Exercise 4

It shows the variable that containing "time" in the character. It is surprising because it shows the variables that has differences in capitalization. 
```{r}
select(flights, contains("TIME"))
```

## R4DS 5.5.2

### Exercise 1

```{r}
mutate(flights, dep_time_mins = dep_time %/% 100 * 60 + dep_time %% 100, sched_dep_time_mins = sched_dep_time %/% 100 * 60 + sched_dep_time %% 100)
```

### Exercise 2

It was expected to see the air_time = dep_time - arr_time. However, the code below does not show my expectations. It is required to fix the time zone difference between the arrival and the departure location.
```{r}
flights_airtime <-
  mutate(flights,
    dep_time = (dep_time %/% 100 * 60 + dep_time %% 100) %% 1440,
    arr_time = (arr_time %/% 100 * 60 + arr_time %% 100) %% 1440,
    dep_arr_time_diff = arr_time - dep_time
  )

select(flights_airtime, air_time, dep_arr_time_diff)
```

### Exercise 3

The relationship is shown from the following equation: 
dep_time - sched_dep_time = dep_delay

```{r}
select(flights, dep_time, sched_dep_time, dep_delay)
```

### Exercise 4

how to rank 
```{r}
flight_delays <- mutate(flights, delay_rank = min_rank(desc(dep_delay)))
filter(flight_delays, delay_rank <= 10)

#Delay rank from 1 to 10
arrange(flight_delays, delay_rank)
```

### Exercise 5

The length of vectors are not the same. It would be same as adding 1, 2, 3 to 1-10 repeatably.
The return is giving a same value as 1+1, 2+2, 3+3, 1+4, 2+5, 3+6, 1+7, 2+8, 3+9, 1+10
```{r}
1:3 + 1:10
```

### Exercise 6

It provides the following trig functions:
cos(x)
sin(x)
tan(x)

acos(x)
asin(x)
atan(x)
atan2(y, x)

cospi(x)
sinpi(x)
tanpi(x)

## R4DS 5.10.5

### Exercise 1

You can tell by printing the packages, or using a function class, or is_tibble(). mtcars shows as a data.frame
```{r}
mtcars
as_tibble(mtcars)
is_tibble(mtcars)
```

### Exercise 2

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

The $ does not show the observation in tibble which used to show in the data frame. Because tibble does not allow autofill correction. The 4th line returns as in a form of a vector not a value. The 5th line returns as same as the data frame since it was inside of the c[].  
```{r}
tbl <- as_tibble(df)

tbl$x
tbl[, "xyz"]
tbl[, c("abc", "xyz")]
```

### Exercise 3

You can extract the reference variable using the double bracket such as df[[var]] or df$'var'

### Exercise 4

```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

annoying

# Extracting the variable called 1.

annoying[['1']]

# Plotting a scatterplot of 1 vs 2.

ggplot(data = annoying, mapping = aes(x = `1`, y = `2`)) +
  geom_point()

# Creating a new column called 3 which is 2 divided by 1.

mutate(annoying, `3` = `2` / `1`)

# Renaming the columns to one, two and three.

annoying <- rename(annoying, one = `1`, two = `2`)
mutate(annoying, three = `two` / `one`)
```
