---
title: "Homework 1"
author: "Jin Gyu Kim"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercises

## R4DS 27.2.1

### Exercise 1
I created a new notebook using File > New File > R Notebook. 
I read the instructions, practiced running the chunks by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 
I modified the code to *summary(cars)* and re-run it, and see modified output.

### Exercise 2
I created a new R Markdown document using File > New File > R Markdown. I knitted it by clicking the appropriate button, and using keyboard short cut pressing *Cmd+Shift+K*.
I modified the input and saw the output update.

### Exercise 3
When running the plot(), R markdown and R notebook both shows their output inside the editor. When running summary(), R markdown and R notebook both shows their output inside the editor and inside the console. There were no difference between R markdown and R notebook in the output. 

Both R markdown and R notebook can be knit to produce HTML, PDF, and docx extension, only R notebook has preview with the extension .nb.html. Both requires to save before knitting, while R notebook doesn't.

R markdown initially has *title, author, date,* and *output - html_document*, but R notebook has only *title,* and *output - html_notebook*. Copying YAML from one to another is interchangeable, however, it changes a file by the *output* in the header. 

### Exercise 4

When knitting to PDF or docx, the *pdf_document: default, word_document: default* has been added below *html_document: default* input in YAML. 

YAML header in PDF and docx were in the middle line and split to two pages, while html YAML header stayed in the left side with a single plage. The color of header changed to blue when knitted to only docx output. 

## R4DS 27.3.1

### Exercise 1

## Jin Gyu Kim

***
### Employment
***
* Classroom Technology Student Assistant (OSU College of Pharmacy) **Aug 2021 - Present**


* Online Private Tutor (Glorang) **May 2021 - Present**


* Medic/Squad Leader (Republic of Korea Army) **Aug 2019 - Mar 2021**

* Pharmacy Technician (Medication Management Program) **Oct 2017 - Nov 2018**


### Education
***
* The Ohio State University (PharmD) **Aug 2021 - Present**


* Armed Force Military Medical School (Student President) **Sep 2019 - Oct 2019**


* The Ohio State University (BA Chemistry) **Aug 2015 - May 2019**

### Exercise 2

1. Add a footnote.

This is a sentence that has a footnote^[This is a footnote] 

2. Add a horizontal rule.

This is a horizontal rule below.

*** 

3. Add a block quote.

> This is a block quote


### Exercise 3

```{r setup1, include = FALSE}
library(ggplot2)
library(dplyr)
smaller <- diamonds %>% 
  filter(carat <= 2.5)
```

We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

The most striking feature is, the most diamonds are placed between 0.25 - 0.5 carats

# Practices 

## R4DS 4.4

### Practice 1 

It didn't work because of the letter 'ı' below is not the same letter 'i' above.

### Practice 2

This is the fixed version from the question

```{r}

library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)

```

### Practice 3

When I pressed *Alt + Shift + K*, it showed me a keyboard shortcuts. You can find the same thing by clicking the menu *tools* -> *Keyboard Shortcuts Help*

# Additional exercises

Here are the rows of the mtcars dataset corresponding to Honda and Toyota cars.

```{r additional exercise, echo = TRUE}

knitr::kable(
  mtcars[19:21, ],
  caption = "A knitr kable.",
  )

```
